---
title: "qPCR processing for FunExp"
output: html_document
date: "2023-03-07"
---

# Set up and Load data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load libraries
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(car)
```
## Plot themes
```{r}
# with legend
Theme=theme_classic(base_size=11, base_family="Helvetica") +
  theme(axis.line = element_line(size = 1, colour = "black", linetype = "solid")) +theme(plot.title = element_text(size = 12))
# without legend
Theme2=Theme+ theme(legend.position="none") + theme(panel.border=element_rect(fill=NA))
```

## Data
Data from qPCR: load and process.
```{r}
qPCR_data1=read.csv('input_data/qPCR/FunEx1_calculations.csv', header=TRUE)
qPCR_data2=read.csv('input_data/qPCR/FunEx2_calculations.csv', header=TRUE)
# merge
qPCR_dataAll=rbind(qPCR_data1, qPCR_data2)
# specify class
qPCR_dataAll$age=as.numeric(qPCR_dataAll$age)
# make column with sample name
qPCR_dataAll$sample_name=paste(qPCR_dataAll$agetreatment, qPCR_dataAll$treatment, qPCR_dataAll$replicates, sep='_')
```

Identify and remove outliers.
Outliers defined as higher than 2* 10^6 copies.
```{r}
qPCR_clean=qPCR_dataAll[-which(qPCR_dataAll$Quantity>2000000),]
```

# Analysis
Focus on 2 relationships:
* gene copy abundance and leaf age
* gene copy abundance and diversity
* gene copy abundance and function

## gene counts vs leaf age
If bacterial abundance changes dramatically with leaf age, functional activity and bacterial diversity may be impacted by abundance alone. 

### Plot
```{r}
plot_qpcrage=ggplot(qPCR_clean, aes(age, log(Quantity+1))) + geom_jitter() + Theme2 +
  xlab('leaf age (weeks)') + ylab('log(16S rRNA gene copy number +1)') + 
  annotate('text', x=1, y=14, label='a. ')
```

### Test for statistical differences:
```{r}
# anova neg but does not seem normally distributed
qPCR_Funexp_anova=aov(log(Quantity+1)~age, data=qPCR_clean)
summary(qPCR_Funexp_anova)
shapiro.test(residuals(qPCR_Funexp_anova))
qqplot(predict(qPCR_Funexp_anova), residuals(qPCR_Funexp_anova))

# non parametric
kruskal.test(log(Quantity+1)~age, data=qPCR_clean)
```

glm version
```{r}
qPCR_Funexp_mod=lm(log(Quantity+1)~age, data=qPCR_clean)
summary(qPCR_Funexp_mod)
Anova(qPCR_Funexp_mod)

```

## gene abundance vs species diversity
Load diveristy data:
```{r}
ASVtable.fundiv=read.table('input_data/ASVtable_forGLM_FunExp12023-01-04.txt', header=TRUE)
metatable=ASVtable.fundiv[,1377:1394]
metatable2=metatable[-which(is.na(metatable$Tube_name)),]
metatable2$sample_name=paste(metatable2$leaf_age, metatable2$treatment, metatable2$replicates, sep='_')
meta_qPCR=left_join(metatable2, qPCR_clean)

meta_qPCR_clean=meta_qPCR[-which(is.na(meta_qPCR$Quantity)),]

```

### plot

```{r}
plot_qpcrrich=ggplot(meta_qPCR_clean, aes((Quantity), richness)) + geom_point() + Theme2 +annotate('text', x=-0.5, y=100, label='b.') + xlab('16S rRNA gene copy number') +
  ylab('ASV richness') 
```

### statistics
glm version - stat test
```{r}
qPCRrichness_mod=lm(richness~(Quantity+1), data=meta_qPCR_clean)
summary(qPCRrichness_mod)
```

## gene abundance vs function
### plot
```{r}
plot_qpcrFun=ggplot(data=meta_qPCR_clean, aes(x=Quantity, y=W_Change)) + geom_point() + Theme2 + annotate('text', x=-0.5, y=0.030, label='c.') + xlab('16S rRNA gene copy number') +
  ylab('Weight change (g)')
```
### stats
glm version - stat test
```{r}
qPCRFun_mod=lm(W_Change~(Quantity+1), data=meta_qPCR_clean)
summary(qPCRFun_mod)

```

## Merge plots
```{r}
library(gridExtra)
grid.arrange( plot_qpcrage, plot_qpcrrich, plot_qpcrFun, ncol=3)
```

