---
title: "FunASV_v8_taxAnalysis_abund-functB"
date: "2022-12-23"
output: 
  html_document:
    toc: TRUE
---
## Evaluating ASV contributions to function in FunExp
The goal of this script is to establish the trends in community composition change along the successional processes in Sarracenia purpurea microbial community - with a focus on single species or taxon. Then, we establish their likely functional contribution using functional means.

This analysis goes along a functional analysis of the communities ability to degrade insect prey.

To this aim, the species abundance data is sorted into a long format for iterative GLMs. This will identify species that increase with leaf age. Then, these select species are regressed against functional means to ascertain which ones are most likely contributing to degradative functions. 

## Preparation
### Load libraries and establish a plotting theme
```{r message=FALSE}
# Libraries
library(ggplot2)
library(gridExtra)
library(dplyr)

# Plot themes
## With legend
Theme=theme_classic(base_size=11, base_family="Helvetica") +
	theme(axis.line = element_line(size = 1, colour = "black", linetype = "solid")) +theme(plot.title = element_text(size = 12))
## Without legends
Theme2=Theme+ theme(legend.position="none") + theme(panel.border=element_rect(fill=NA))
```

Set up the saving parameters: an path for the folder and the date and time for unique files.
```{r}
outPATH='output_tables/'
date=Sys.Date()
```

### Second, load the datasets:
* ASVtable.fundiv contains ASV(code) relative abundances, functional data and diversity data for each sample
* taxtable contains taxonomic affiliation per ASVcode
```{r}
ASVtable.fundiv=read.table('input_data/ASVtable_forGLM_FunExp12023-01-04.txt', header=TRUE)
  ASVtable.fundiv1=ASVtable.fundiv[,-1]
taxatable=read.table('input_data/taxtable_FunExp12023-01-04.txt', header=TRUE)
```

### 1.Iterate the GLM:
Now build an iterative model function:
* glm (gaussian distribution) vs null model
* Store the model's outputs and the comparison with the null. 

Input:
* wide format dataset with ASV, fundiv data: ASVtable.fundiv1
* list of taxa with number, DNA sequence, taxonomic affiliation and organized from more abundant to least abundant: taxatable

```{r echo=FALSE, include=FALSE}
IterativeGLM_Fun <- function(ASVfun, taxatable){
  ASVfun_names=names(ASVfun)[1:1375]
# create objects to store model results
  model.glmFun.results=c() # store model coefficients and output
  model.glmFun.evaluation=c() # store comparison between models

for (i in 1:length(ASVfun_names)) {
  ASVdataFun=(ASVfun[,c(i,1376:1393)])
  names(ASVdataFun)[1]='ASVrelabun'
  
    # skip columns with 0 to 4 appearances
  ASVdataFun_presence=ASVdataFun[1]
  ASVdataFun_presence[which(ASVdataFun_presence>1),]=1
  if (sum(ASVdataFun_presence)<5) {print('low occurrence (<2)')} else {
      
    tax_rownum=which(taxatable$ASVcode==ASVfun_names[i])
  
    # data clean up steps   
        if (length(which(ASVdataFun$ASVrelabun==0))>0) {
          ASVdataFun=ASVdataFun[-which(ASVdataFun$ASVrelabun==0),] } else {print('nope')}
        if (length(which(is.na(ASVdataFun$W_Change)))>0) {
          ASVdataFun=ASVdataFun[-which(is.na(ASVdataFun$W_Change)),] } else {print('nope2')}
  
    # Check progress
      print(paste('Progress:', (ASVfun_names[i]), 
        (taxatable$Family[tax_rownum]),
        (taxatable$Genus[tax_rownum]), sep=' '))
  
    # Model runs
      # GLM with gaussian distribution
        Mod.fun1=lm(W_Change ~ ASVrelabun, data=ASVdataFun)
	  		  Mod1.summary=summary(Mod.fun1)
		  	  Mod1.coeff=Mod1.summary$coefficients
	    # Null model
	      Mod.null=glm(W_Change ~ 1, data=ASVdataFun)
	  
      # Model comparison
		    Mod1.aov=anova(Mod.fun1, Mod.null, test='Chisq')
		    aic.model=AIC(Mod.fun1,Mod.null)		
  
	  # Store coefficients
		  coeff.full.model = data.frame((Mod1.summary$coefficients), 
		                              adj.p=p.adjust(Mod1.summary$coefficients[,2]), 
		                              Family=rep(taxatable$Family[tax_rownum],2),
		                              Genus=rep(taxatable$Genus[tax_rownum],2),
		                              ASVcode=rep(ASVfun_names[i],2), 
		                              ASVseq=rep(taxatable$ASVseq[tax_rownum], 2)) 
	  # Store comparison
		  coeff.aov = data.frame(model=c(paste(ASVfun_names[tax_rownum], 'null.model', sep='_'),
		                               paste(ASVfun_names[tax_rownum], 'full.model', sep='_')), 
		                       resid.df=Mod1.aov[1], resid.dev=Mod1.aov[2], deviance=Mod1.aov[[4]], 
		                       AIC=aic.model$AIC, chisq.p=Mod1.aov[[5]], adj.p=p.adjust(Mod1.aov[[5]]), 
		                       Family=rep(taxatable$Family[tax_rownum],2) ,
		                       Genus=rep(taxatable$Genus[tax_rownum],2), 
		                       ASVcode=rep(ASVfun_names[i],2),
		                       ASVseq=rep(taxatable$ASVseq[tax_rownum],2))		
	
	  # format results table
		  model.glmFun.results=(rbind(model.glmFun.results, coeff.full.model)) 		
		  model.glmFun.evaluation=(rbind(model.glmFun.evaluation, coeff.aov))		
                                                }
                                  }
    # Finalize output:
    dim(model.glmFun.results) # check for expected dimensions
    # Add names to the columns of output tables:
    names(model.glmFun.results)=c('Estimate', 'Serror', 't.value', 'p.value', 'p.adjust','Family', 'Genus', 'ASVcode','ASVseq')
    names(model.glmFun.evaluation)=c('Model', 'df', 'Resid.dev', 'Deviance',  'AIC', 'p.value','adjust.p', 'Family', 'Genus', 'ASVcode','ASVseq')
    
    # Store both objects within a list
    model.results.output.glmFun=list(coefficients=model.glmFun.results, evaluation=model.glmFun.evaluation)

return(model.results.output.glmFun)
}
```

### 2. Run model
Run the function with all ASVs
```{r include=FALSE}
model.results.trial1=IterativeGLM_Fun(ASVtable.fundiv1, taxatable)
```

Clean and save the output of the function: these tables will go to supplementary materials. 
```{r eval=FALSE}
models.coefficients1 = model.results.trial1$coefficients
models.evals1 = model.results.trial1$evaluation

    glm.models.coeff = paste(outPATH, 'ASV_glm_coefficients_FunExp1', date,'.txt', sep='')
    glm.models.evals = paste(outPATH, 'ASV_glm_evals_FunExp1', date,'.txt', sep='')

#write.table(models.coefficients1, glm.models.coeff, sep="\t")
#write.table(models.evals1, glm.models.evals, sep="\t")
```

### 3. Sort through the output tables:
Save one list with those taxa that have significant positive slopes with function, and one of those who do not. 
```{r include=FALSE}
# create lists to store potential ASVs correlated with function
list_asv_slopePos.Fun=c()
list_asv_noslope.Fun=c()
list_asv_slopeNeg.Fun=c()

# list of ASV codes to go through:
ASVfun_names=names(ASVtable.fundiv1)[1:1375]

for (i in 1:length(ASVfun_names)){
  # check that the ASV is present in the dataset
  if (sum(which(models.coefficients1$ASVcode==ASVfun_names[i]))==0) { print(paste(ASVfun_names[i], 'ASV not found'))
    } else {
  
    # extract the slope estimate:
      ASVabund.estimate= models.coefficients1[which(models.coefficients1$ASVcode==ASVfun_names[i]),1][2]
    # extract the p value:
      ASVabund.p= models.coefficients1[which(models.coefficients1$ASVcode==ASVfun_names[i]),5][2]
      ASVcode= models.coefficients1[which(models.coefficients1$ASVcode==ASVfun_names[i]),8][2]
      ASVGenus= models.coefficients1[which(models.coefficients1$ASVcode==ASVfun_names[i]),6][2]
      
    # inform of progress:  
      print(paste('Progress:', i, ASVcode, ASVGenus))
    
    # check that output differs from NA
      if (is.na(ASVabund.p)) { 
          print(paste(ASVfun_names[i], 'p value was NA'))
          list_asv_noslope.Fun=rbind(list_asv_noslope.Fun, c(ASVfun_names[i], ASVabund.estimate, ASVabund.p))
                             } else {
        
    # Sort the taxa
      # if the taxa has a positive slope estimate and a significant adjusted p value -> accept and store ASVcode
        if (ASVabund.estimate > 0 && ASVabund.p < 0.05 ) {
          list_asv_slopePos.Fun=rbind(list_asv_slopePos.Fun, c(ASVfun_names[i], ASVabund.estimate, ASVabund.p))
            } else   { 
       # if the taxa has a negative slope estimate and a significant adjusted p value -> accept and store ASVcode
        if (ASVabund.estimate < 0 && ASVabund.p < 0.05 ) {
          list_asv_slopeNeg.Fun=rbind(list_asv_slopeNeg.Fun, c(ASVfun_names[i], ASVabund.estimate, ASVabund.p))
            } else {
       # store non significant and NA results ASV in noslope list
        list_asv_noslope.Fun=c(list_asv_noslope.Fun, paste(ASVfun_names[i], ASVabund.estimate, ASVabund.p)) 
                   }
                    } 
                                }
                                }
        }

```

#### Edit the sorted tables and save
Change from matrix to data frame and add column names.
Focus on negative and positive slopes from here on. 
```{r}
list_asv_slopePos.Fun.df=data.frame(list_asv_slopePos.Fun)
  colnames(list_asv_slopePos.Fun.df)=c('ASVcode', 'ASVestimate', 'ASVp.value')
  listPos.rank=list_asv_slopePos.Fun.df[order(list_asv_slopePos.Fun.df$ASVestimate),]
  
list_asv_slopeNeg.Fun.df=data.frame(list_asv_slopeNeg.Fun)
  colnames(list_asv_slopeNeg.Fun.df)=c('ASVcode', 'ASVestimate', 'ASVp.value')
  listNeg.rank=list_asv_slopeNeg.Fun.df[order(list_asv_slopeNeg.Fun.df$ASVestimate),]
  
list_asv_noslope.Fun.df=data.frame(list_asv_noslope.Fun)
  colnames(list_asv_noslope.Fun.df)=c('ASVcode', 'ASVestimate', 'ASVp.value')
  listnoslope.rank=list_asv_noslope.Fun.df[order(list_asv_noslope.Fun.df$ASVestimate),]
```


Merge the lists with their taxonomic affiliations
```{r}
listPos.rank_taxa=left_join(listPos.rank, taxatable)
listnoslope.rank_taxa=left_join(listnoslope.rank, taxatable)
listNeg.rank_taxa=left_join(listNeg.rank, taxatable)

```
Save them as a single table
```{r}
 ASVslope.sorted=rbind(
    data.frame(Slope=rep('Positive',dim(listPos.rank_taxa)[1]), listPos.rank_taxa),
    data.frame(Slope=rep('Neutral',dim(listnoslope.rank_taxa)[1]), listnoslope.rank_taxa),
    data.frame(Slope=rep('Negative',dim(listNeg.rank_taxa)[1]), listNeg.rank_taxa))
    
ASVslope.sorted_path = paste(outPATH, 'ASVslope_sorted_FunExp1', date,'.txt', sep='')

	#write.table(ASVslope.sorted, ASVslope.sorted_path, sep="\t")
```
